% !TEX root = ../my-thesis.tex
%
\pdfbookmark[0]{Acknowledgements}{Acknowledgements}
\addchap*{Acknowledgements}
\label{sec:acknowledgements}

Even after eight years at university, it still feels \emph{surprising} to see myself writing this PhD thesis and reaching this stage in my life. This thesis is for every LGBTQ+ child who grew up thinking the world is not for them.

I will forever be indebted and grateful to the many, many people without whom I would never be here. There are so many people I have to thank on my PhD journey and I can barely cover them all here -- but I'll try!

Firstly, I thank everyone who has contributed to the academic side of the this thesis in Heidelberg. To my supervisor Sabine Reffert, thank you so much for your guidance and support throughout my PhD. Your eye for detail pushed me to strive for excellence in my work and helped to improve the quality of my research. Your input and feedback were invaluable, and without your expertise, I would not have been able to produce the high-quality science that I am proud to include in this thesis. In addition, I thank a number of people who have given up time to help with my project: Anna Pasquali and Andreas Quirrenbach, for their helpful comments and support on my thesis committee; Hans-Walter Rix for agreeing to be the second referee of this thesis; as well as Ralf Klessen and Matthias Bartelmann for agreeing to be the third and fourth examiners at my thesis defence. 

Next, I thank a number of people without whom I never would have reached the start of this PhD. Michelle Cuthbert, your phenomenal commitment and passion for teaching had an impact on me that I will carry with me for the rest of my life. I still remember my first lesson of Year 12 physics, where you asked those of us intending to study physics at university to raise our hands. I think one or two hands were raised, of which I was not one. You proudly remarked that you would change our minds in the twelve months before we had to finalise our university and course applications. By the end of Year 13, a majority of our class went on to study physics -- in no small part thanks to your teaching. I would never have studied physics -- let alone go on to do a PhD -- had I never been exposed to your infectiously passionate physics teaching.

Victoria Scowcroft, the summer project I did with you was a fantastic introduction to \gaia, statistics, and astronomy research that I cherish to this day. Your mentorship and guidance helped me to fall in love with doing research, and your humour helped me see how fun working in this field can be. I am eternally thankful for the sense of belonging in this field that you instilled in me.

Stijn Wuyts, thank you for your fantastic guidance and advice during my master's project. I had so much fun working on the project and I'm very thankful to you for introducing me to machine learning, something we worked together to discover more about. In particular, your scientific and methodical approach to solving problems is something I still aim for today. Your supervision and approach had a big impact on my abilities as a scientist.

To the PhD students at the University of Bath that I met during my final year -- Abi, Anastasia, Bruno, Caroline, Charlotte, Eliot, and Nuria -- thank you so much for adopting me into your lunch group and giving me so much insight. I learnt so much from you all about what a PhD entails and where I could go to do one. I would definitely have never applied abroad to do a PhD without you all.

Finally, there are so many friends I've relied on along the way during my PhD, all of whom have been instrumental in motivating me across the finish line. To Loke and Laura, thank you so much for being such good friends throughout my PhD. I am so glad that we met when we all moved here to Heidelberg. It has been a tough few years thanks to the pandemic, but your friendship and motivation were a huge help in getting me across the finish line.

To my friends back in the UK -- especially Claire, Jordan, Kate, and Mathy, along with everyone else I know from Backstage at the Bath Students' Union -- thank you so much for always being amazing friends, and especially for all of the fun times we still managed to have even despite the pandemic. I miss you all constantly. I'm so happy I get to see you more regularly once again, even though it's still nowhere near often enough.

To the community at LSW and the PhD students in the IMPRS as a whole, thank you for being awesome. There are so many lovely people that I've been lucky enough to meet and learn from over the past four years. Thank you to all of you for the chats, the advice, and the fun. Especially thank you to everyone in the North building at LSW, who made me feel so welcome here right from my very first day. A special thank you goes to Dane for agreeing to proof read the German part of my abstract.

Finally, from the bottom of my heart, thank you Zoe. You have been instrumental in motivating me to finish and brightening up every single day of my life since I met you here in Heidelberg. (And also in writing the German abstract for my thesis!) I'm so excited to see what the future holds, because I get to do it all with you.
